---
output: 
#  bookdown::html_document2: 
#  bookdown::pdf_document2:
  bookdown::word_document2:
    keep_tex: yes
    keep_md: yes
    toc: false
    number_sections: false
#bibliography: NECCC-test.bib
---

```{r , include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.dim = c(10, 6), fig.fullwidth=TRUE)
library(readr) # for read_csv
library(emmeans) # for join_test
library(ggResidpanel)
library(tidyverse)
library(kableExtra)
library(ggplot2); theme_set(theme_bw())
library(flextable)
library(patchwork)
library(magrittr)
```

Arithmetic means of crop and weed biomass (g/m$^{-2}$) are in Figure \@ref(fig:summ).  

```{r summ, echo = FALSE, fig.cap = "Arithmetic means of crop and weed biomass."}
fsb.long <- read_csv("../2-Data/Clean/fsb_long.csv")


fsb.long %>% 
  group_by(treatment, species) %>%
    summarise(biomass = mean(biomass.g.per.m.sq),
    sd = sd(biomass.g.per.m.sq),
    n = n(),
    se = sd / sqrt(n)) %>%
  mutate(tag = ifelse(species %in% c("Control", "Weeds"), "Weed", "Crop")) %>% 
  ggplot(aes(x = species, y = biomass, fill = tag)) +
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar( aes(x = species, ymin = biomass - sd, ymax = biomass + sd), width=0.4, colour="black", alpha=0.9, size=1) + 
  ylab(expression(paste("Raw mean biomass (",g~m^{"-2"},")"))) +
  xlab(" ") + 
  facet_grid( ~ treatment, space = "free", scale = "free") + 
   theme(legend.title= element_blank()) + 
  scale_x_discrete(guide = guide_axis(angle = 40)) 
```


```{r, include=FALSE}
fsb <- read_csv("../2-Data/Clean/fsb_wide.csv")
```

```{r include=FALSE, eval=FALSE}
fsb.crops <- fsb %>% filter(species.x != "Control")

find_outlier <- function(x) {
  return(x < quantile(x, .25) - 1.5*IQR(x) | x > quantile(x, .75) + 1.5*IQR(x))
}

fsb %>%
  group_by(block) %>% 
        mutate(outlier = ifelse(find_outlier(weed.biomass.g.per.sq.m), block.f, NA)) %>%
  ggplot(aes(x = treatment, y=weed.biomass.g.per.sq.m)) +
  geom_boxplot() 
```


### Model diagnosis 

Using `ggResidpanel` version 0.3.0 (Goode and Rey, 2019) for model diagnosis, no predictable pattern in the plots of residuals vs. predicted values suggests that the analysis models fit the data well (Figures \@ref(fig:diag-crops) and \@ref(fig:diag-weeds)), but AIC values of the ANCOVA models were lower than those of the ANOVA models: 486 vs. 494 for crop responses in ANCOVA vs. ANOVA; and 182 vs. 194 for weed biomass responses in ANCOVA vs ANOVA.   


### Crop biomass in response to treatment and weed biomass 

```{r response-crops, include = FALSE}
# Worsen the residual plot look
# crops.lm <- lm( log(crop.biomass.g.per.sq.m + min(crop.biomass.g.per.sq.m[crop.biomass.g.per.sq.m > 0]))  ~ as.factor(block) + 
#                   treatment +
#                   log(weed.biomass.g.per.sq.m +  min(weed.biomass.g.per.sq.m[weed.biomass.g.per.sq.m  > 0])),
#                 data = fsb)

# No improvement compared to no data transformation 
# crops.lm <- lm(sqrt(crop.biomass.g.per.sq.m ) ~ as.factor(block) + treatment + weed.biomass.g.per.sq.m, data = fsb)

# resid_panel(crops.lm)
```

```{r diag-crops-ancova, fig.cap = "Diagnosis plot for the ANCOVA and ANOVA models of crop biomass responses"}
fsb.crops <- fsb %>% filter(!treatment %in% c("N", "P", "O")) # Control treatments had no crop
crops.lm1 <- lm(crop.biomass.g.per.sq.m  ~ as.factor(block) + treatment + weed.biomass.g.per.sq.m, data = fsb.crops)


crops.lm2 <- lm(crop.biomass.g.per.sq.m  ~ as.factor(block) + treatment , data = fsb.crops)
resid_panel(crops.lm2)


list(crops.lm1, crops.lm2) %>% 
  lapply(resid_panel, nrow = 2) %>% 
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# AIC(crops.lm1, crops.lm2)
```


### Weed biomass in response to treatment and crop biomass - ANCOVA
```{r diag-weeds, fig.cap = "Diagnosis plot for the linear model of weed biomass responding to treatment and crop biomass"}

## Transforming crop.biomass.g.per.sq.m may be unnecessary because the Control treatment was mean to be zero for crop biomass 
# min(fsb$weed.biomass.g.per.sq.m[fsb$weed.biomass.g.per.sq.m > 0]) #9.24

weeds.lm1 <- lm(log(weed.biomass.g.per.sq.m + 1) ~ as.factor(block) + treatment + crop.biomass.g.per.sq.m, data = fsb)


weeds.lm2 <- lm(log(weed.biomass.g.per.sq.m + 1) ~ as.factor(block) + treatment , data = fsb)

list(weeds.lm1, weeds.lm2) %>% 
  lapply(resid_panel, nrow = 2) %>% 
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# AIC(weeds.lm1, weeds.lm2)

```

### Results  

Weed suppression from different *Brassicacaea* species was comparable among each other and with the control treatments (Table \@ref(tab:anova-weeds)), even though crop biomass differed by species (Table \@ref(tab:anova-crops)). Crop biomass was the strongest factor affecting weed biomass (Table \@ref(tab:anova-crops)).

```{r ancova, include=FALSE}
#Make a side by side table 
crops.ancova <- joint_tests(crops.lm1) %>% print(export = TRUE)
weeds.ancova <- joint_tests(weeds.lm1) %>% print(export = TRUE)
```

```{r, eval=FALSE, include=FALSE}
cbind( weeds.ancova$summary, crops.ancova$summary) %>%
  kable(caption = "ANCOVA tables of crop and weed responses") %>%
  add_header_above(c(" " = 1,  "Weed" = 5, "Crop" = 5))
```

```{r ancova-weeds, echo=FALSE}
weeds.ancova.df <- as.data.frame(weeds.ancova$summary)

weeds.ancova.df %>%
  flextable() %>%
  set_caption("ANCOVA for weed biomass response. Weed biomass was transformed with ln(x + 1) to maintain data normality.")
```

```{r ancova-crops, echo=FALSE}
crops.ancova.df <- as.data.frame(crops.ancova$summary)

crops.ancova.df %>%
  flextable() %>%
  set_caption("ANCOVA for crop biomass response. Crop biomass analyzed on the original scale.")
```

```{r anova, include=FALSE}
#Make a side by side table 
crops.anova <- joint_tests(crops.lm2) %>% print(export = TRUE)
weeds.anova <- joint_tests(weeds.lm2) %>% print(export = TRUE)
```

```{r, eval=FALSE, include=FALSE}
cbind( weeds.anova$summary, crops.anova$summary) %>%
  kable(caption = "ANOVA tables of crop and weed responses") %>%
  add_header_above(c(" " = 1,  "Weed" = 5, "Crop" = 5))
```

```{r anova-weeds, echo=FALSE}
weeds.anova.df <- as.data.frame(weeds.anova$summary)

weeds.anova.df %>%
  flextable() %>%
  set_caption("ANOVA for weed biomass response. Weed biomass was transformed with ln(x + 1) to maintain data normality.")
```

```{r anova-crops, echo=FALSE}
crops.anova.df <- as.data.frame(crops.anova$summary)

crops.anova.df %>%
  flextable() %>%
  set_caption("ANOVA for crop biomass response. Crop biomass analyzed on the original scale.")
```


```{r, echo=FALSE}
weeds.emm <- emmeans(weeds.lm1, "treatment", type = "response")

#weeds.emm 

# emmip(weeds.lm, treatment ~ crop.biomass.g.per.sq.m, cov.reduce = range)

weeds_labels <- c("Radish",
"Turnip",
"Rapeseed",
"Collard", 
"Broadleaf Mustard",
"Mustard",
"Brown mustard", 
"Oriental Mustard",
"Arugula",
"Winter Camelina",
"Kale",
"Red Clover",
"Alfalfa", 
rep("Control", 3))

crops_labels <- c("Radish",
"Turnip",
"Rapeseed",
"Collard", 
"Broadleaf Mustard",
"Mustard",
"Brown mustard", 
"Oriental Mustard",
"Arugula",
"Winter Camelina",
"Kale",
"Red Clover",
"Alfalfa")
```

```{r, eval=FALSE, include=FALSE}
weeds.lm2 <- lm(weed.biomass.g.per.sq.m  ~ as.factor(block) + treatment + crop.biomass.g.per.sq.m, data = fsb)
joint_tests(weeds.lm2)
resid_panel(weeds.lm2)
```

```{r, eval=FALSE, include=FALSE}
weeds.lm3 <- lm(log(weed.biomass.g.per.sq.m +  min(weed.biomass.g.per.sq.m[weed.biomass.g.per.sq.m > 0]))  ~ as.factor(block) +  crop.biomass.g.per.sq.m, data = fsb)
joint_tests(weeds.lm3)
resid_panel(weeds.lm3)
```

```{r, eval=FALSE, include=FALSE}
weeds.lm4 <- lm(log(weed.biomass.g.per.sq.m +  min(weed.biomass.g.per.sq.m[weed.biomass.g.per.sq.m > 0]))  ~ as.factor(block) +  treatment, data = fsb)
joint_tests(weeds.lm4)
resid_panel(weeds.lm4)
```

Estimated marginal means of weed and crop biomass in each treatment are shown in Figures \@ref(fig:weed-contrast) and \@ref(fig:crop-contrast).    


```{r weed-contrast, echo=FALSE, fig.cap= "Estimated marginal means of weed biomass (back transformed from ln(x +1)."}

weeds.emmip <- emmip(weeds.lm1, ~ treatment, type = "response", plotit = FALSE)
weeds.emmip %>% 
  mutate(sd = 2*SE) %>%
  ggplot(aes(x = treatment, y = yvar)) +
  geom_bar(stat="identity") + 
  geom_errorbar( aes(x=treatment, ymin=yvar-sd, ymax=yvar+sd), width=0.4, colour="orange", alpha=0.9, size=1.3) + 
  ylab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  xlab("Treatment") + 
  scale_x_discrete(guide = guide_axis(angle = 40), labels = weeds_labels)
  
```


```{r weed-contrast4, eval=FALSE, include=FALSE}
plot(emmeans(weeds.lm4, "treatment"), comparisons = TRUE) + 
  xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment")
```

```{r crop-contrast, echo=FALSE, fig.cap= "Estimated marginal means of crop biomass."}
crops.emmip <- emmip(crops.lm1, ~ treatment , type = "response", plotit = FALSE)
crops.emmip %>% 
  mutate(sd = 2*SE) %>%
  ggplot(aes(x = treatment, y = yvar)) +
  geom_bar(stat="identity") + 
  geom_errorbar( aes(x =  treatment , ymin = yvar-sd, ymax = yvar+sd), width=0.4, colour="orange", alpha=0.9, size=1.3) + 
  ylab(expression(paste("Crop biomass (",g~m^{"-2"},")"))) +
  xlab("Treatment") + 
  scale_x_discrete(guide = guide_axis(angle = 40), labels = crops_labels)
```

The arrow plots below (Figures \@ref(fig:weed-emmip) and \@ref(fig:crop-emmip)) convey the same information with the bar charts, but quicker to make. 

```{r weed-emmip, echo = FALSE, fig.cap= "Estimated marginal means of weed biomass (back transformed from ln(x +1)). The black dots are the estimated marginal means. The blue bars indicate the estimated 95% confidence intervals. The arrows indicate whether two estimated means were significantly different. Overlapping arrows means non-significant difference."}
## emmip
# plot(emmeans(weeds.lm, "treatment", type = "response"), comparisons = TRUE) + 
#   xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
#   ylab("Treatment")


plot(emmeans(weeds.lm1, "treatment", type = "response"), comparisons = TRUE) + 
  xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment") + 
  scale_y_discrete(labels = weeds_labels)
```

```{r crop-emmip, echo = FALSE, fig.cap= "Estimated marginal means of crop biomass. The blue bars indicate the estimated 95% confidence intervals. The black dots are the estimated marginal means. The arrows indicate whether two estimated means were significantly different. Overlapping arrows means non-significant difference."}
plot(emmeans(crops.lm1, "treatment"), comparisons = TRUE) + 
  xlab(expression(paste("Crop biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment") + 
  scale_y_discrete(labels = crops_labels)
```