---
output: 
  bookdown::html_document2: 
#  bookdown::pdf_document2:
#  bookdown::word_document2:
    keep_tex: yes
    keep_md: yes
    toc: false
    number_sections: false
#bibliography: NECCC-test.bib
---

```{r , include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      fig.dim = c(10, 6), 
                      fig.fullwidth=TRUE, 
                      dev = "jpeg",
                      dpi = 900)
#https://github.com/tidyverse/ggplot2/pull/3833 
opts <- options(
  ggplot2.discrete.fill = list(
    c("#B31B1B", "#006699"),
#    RColorBrewer::brewer.pal(3, "Set2"),
#    RColorBrewer::brewer.pal(6, "Accent"),
    RColorBrewer::brewer.pal(12, "Paired") # doesn't change the nls-plot color
  )
)

library(readr) # for read_csv
library(emmeans) # for join_test
library(ggResidpanel)
library(tidyverse)
library(kableExtra)
library(ggplot2); theme_set(theme_bw())
library(flextable)
library(patchwork)
library(magrittr)
library(nls2)
library(nlstools)
library(RColorBrewer) #for brewer.pal
```

Arithmetic means of crop and weed biomass (g/m$^{-2}$) are in Figure \@ref(fig:summ).  
```{r summ, echo = FALSE, fig.cap = "Arithmetic means of crop and weed biomass."}
fsb.long <- read_csv("../2-Data/Clean/fsb_long.csv")

# Make sure that the levels are kept  

#levels(factor(fsb.long$treatment))   #A B C D E F G H I J K L N

fsb.long %>% 
  group_by(treatment, species) %>%
    summarise(biomass = mean(biomass.g.per.m.sq),
    sd = sd(biomass.g.per.m.sq),
    n = n(),
    se = sd / sqrt(n)) %>%
  mutate(tag = ifelse(species %in% c("Control", "Weeds"), "Weed", "Crop")) %>% 
  ggplot(aes(x = species, y = biomass, fill = tag)) +
  geom_bar(stat = "identity", position = "dodge") + 
  geom_errorbar( aes(x = species, ymin = biomass - sd, ymax = biomass + sd), width=0.4, colour="black", alpha=0.9, size=1) + 
  ylab(expression(paste("Raw mean biomass (",g~m^{"-2"},")"))) +
  xlab(" ") + 
  facet_grid( ~ treatment, space = "free", scale = "free") + 
   theme(legend.title= element_blank()) + 
  scale_x_discrete(guide = guide_axis(angle = 40)) 
```




```{r, include=FALSE}
fsb.wide <- read_csv("../2-Data/Clean/fsb_wide.csv")
levels(factor(fsb.wide$species.y)) 

# move "None" (bare soil) to the front in all plots

fsb.wide$species.y <- factor(fsb.wide$species.y, levels = c("None",
                                                            "Arugula" ,    
                                                            "Broadleaf mustard",
                                                            "Brown mustard",
                                                            "Collard",
                                                            "Kale",
                                                            "Mustard",
                                                            "Oriental mustard",
                                                            "Radish",
                                                            "Rapeseed",
                                                            "Red clover",
                                                            "Turnip" ))
```


### Results  

Crop biomass was the strongest factor affecting weed biomass (Table \@ref(tab:ancova-crops) so a non-linear regression was fitted for crop - weed competition (Figure \@ref(fig:nls-plot)). Collard's weed suppression was distinctive among all the treatments (Table \@ref(tab:anova-crops).   


```{r raw-competition-scatter, include=FALSE}
fsb.wide %>%
  ggplot(aes(x = crop.biomass.g.per.sq.m, y = weed.biomass.g.per.sq.m, color = treatment)) +
  geom_point() + 
  ylab(expression(paste("Raw mean weed biomass (",g~m^{"-2"},")"))) +
  xlab(expression(paste("Raw mean crop biomass (",g~m^{"-2"},")"))) +
   theme(legend.title= element_blank()) + 
  scale_x_discrete(guide = guide_axis(angle = 40)) 
```

A nonlinear regression was fitted with $Y = \frac{C}{1 + I_w B_c}$, where  

$Y$ is predicted weed biomass,  
$C$ is weed biomass in the control treatment,   
$I_w$ is an estimated coefficient,    
$B_c$ is crop biomass in cover crop treatment  

```{r, echo=FALSE}
# fsb.wide %>% filter(treatment == "N") %>%
#   group_by(treatment) %>%
#   summarize(mean_weed_control = mean(weed.biomass.g.per.sq.m))  # 148
```

```{r nls-plot,echo=FALSE, fig.cap= "Weed suppression from Brassicaceae biomass"}
nls.brassica <-  nls(weed.biomass.g.per.sq.m ~ 148 / (1 + i.w * crop.biomass.g.per.sq.m),
    start = list(i.w = 0),
    data = fsb.wide)

summary(nls.brassica )

# plot(residuals(nls.brassica))

# max(fsb.wide.summ$crop.biomass.g.per.sq.m) #  135.59 
# 
# max(fsb.wide.summ$weed.biomass.g.per.sq.m) # 171.32
fsb.wide.summ <- fsb.wide %>%
group_by(species.y) %>%
 summarise(crop.biomass.g.per.sq.m = mean(crop.biomass.g.per.sq.m),
      weed.biomass.g.per.sq.m = mean(weed.biomass.g.per.sq.m)) 

mannual_pallette <- c(brewer.pal(12,"Paired"))

fsb.wide %>%
ggplot(aes(x = crop.biomass.g.per.sq.m, y = weed.biomass.g.per.sq.m)) +
#  ggplot(aes(x = mean_x, y = mean_y )) +
  geom_line(aes(y=predict(nls.brassica)), size = 2) + 
  geom_point(aes( color = species.y), size = 3, data = fsb.wide.summ ) +
  ylim(28, 190) +
  xlim(0, 170) +
  ylab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  xlab(expression(paste("Crop biomass (",g~m^{"-2"},")"))) +
  geom_vline(xintercept = 85, color = "grey", linetype="dashed") + 
  geom_hline(yintercept = 109, color = "grey", linetype="dashed") + 
#  labs(color= 'Cover crop') + 
  scale_colour_manual(name  ="Cover crop",  #https://stackoverflow.com/questions/66115833/cannot-set-colours-as-values-in-scale-colour-discrete 
                            breaks=c("None",
                                                            "Arugula" ,    
                                                            "Broadleaf mustard",
                                                            "Brown mustard",
                                                            "Collard",
                                                            "Kale",
                                                            "Mustard",
                                                            "Oriental mustard",
                                                            "Radish",
                                                            "Rapeseed",
                                                            "Red clover",
                                                            "Turnip" ),
                            labels = c("None",
                                       "Arugula \n (Eruca vesicaria)" ,
                            "Broadleaf mustard \n (Brassica juncea)",
                            "Brown mustard \n (Brassica juncea)",
                            "Collard \n (Brassica oleracea)",
                            "Kale \n (Brassica oleracea)",
                            "Mustard \n (Sinapis alba)",
                            "Oriental mustard \n (Brassica juncea)",
                            "Radish \n (Raphanus raphanistrum subsp. sativus)",
                            "Rapeseed \n (Brassica napus)",
                            "Red clover \n (Trifolium pratense)",
                            "Turnip \n (Brassica rapa)" ), values = mannual_pallette) +
#   scale_colour_brewer(palette="Paired") +
#  scale_fill_manual(palette = "Paired") +
  theme(text = element_text(size=15))


```





### Linear model diagnosis 

Weed suppression from different *Brassicacaea* species was comparable among each other and with the control treatments (Table \@ref(tab:ancova-weeds)), even though crop biomass differed by species (Table \@ref(tab:ancova-crops)). 

Using `ggResidpanel` version 0.3.0 (Goode and Rey, 2019) for model diagnosis, no predictable pattern in the plots of residuals vs. predicted values suggests that the analysis models fit the data well (Figures \@ref(fig:diag-crops) and \@ref(fig:diag-weeds)), but AIC values of the ANCOVA models were lower than those of the ANOVA models: 448 vs. 459 for crop responses in ANCOVA vs. ANOVA; and 159 vs. 174 for weed biomass responses in ANCOVA vs ANOVA.   


### Crop biomass in response to treatment and weed biomass 

```{r include=FALSE, eval=FALSE}
fsb.crops <- fsb.wide  %>% filter(species.x != "Control")
```

```{r diag-crops, fig.cap = "Diagnosis plot for the ANCOVA and ANOVA models of crop biomass responses"}
fsb.crops <- fsb.wide  %>% filter(treatment != "N") # Control treatments had no crop
crops.lm1 <- lm(crop.biomass.g.per.sq.m  ~ as.factor(block) + species.y + weed.biomass.g.per.sq.m, data = fsb.crops)


crops.lm2 <- lm(crop.biomass.g.per.sq.m  ~ as.factor(block) + species.y , data = fsb.crops)
resid_panel(crops.lm2)


list(crops.lm1, crops.lm2) %>% 
  lapply(resid_panel, nrow = 2) %>% 
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# AIC(crops.lm1, crops.lm2) 448 vs 459
```


### Weed biomass in response to treatment and crop biomass - ANCOVA
```{r diag-weeds, fig.cap = "Diagnosis plot for the linear model of weed biomass responding to treatment and crop biomass"}


weeds.lm1 <- lm(log(weed.biomass.g.per.sq.m + 1) ~ as.factor(block) + species.y + crop.biomass.g.per.sq.m, data = fsb.wide )


weeds.lm2 <- lm(log(weed.biomass.g.per.sq.m + 1) ~ as.factor(block) + species.y , data = fsb.wide )

list(weeds.lm1, weeds.lm2) %>% 
  lapply(resid_panel, nrow = 2) %>% 
  wrap_plots() +
  plot_annotation(tag_levels = "A")

# AIC(weeds.lm1, weeds.lm2) 159 vs 174

```

### Linear models results  

```{r ancova, include=FALSE}
#Make a side by side table 
crops.ancova <- joint_tests(crops.lm1) %>% print(export = TRUE)
weeds.ancova <- joint_tests(weeds.lm1) %>% print(export = TRUE)
```

```{r, eval=FALSE, include=FALSE}
cbind( weeds.ancova$summary, crops.ancova$summary) %>%
  kable(caption = "ANCOVA tables of crop and weed responses") %>%
  add_header_above(c(" " = 1,  "Weed" = 5, "Crop" = 5))
```

```{r ancova-weeds, echo=FALSE}
weeds.ancova.df <- as.data.frame(weeds.ancova$summary)

weeds.ancova.df %>%
  flextable() %>%
  set_caption("ANCOVA for weed biomass response. Weed biomass was transformed with ln(x + 1) to maintain data normality.")
```

```{r ancova-crops, echo=FALSE}
crops.ancova.df <- as.data.frame(crops.ancova$summary)

crops.ancova.df %>%
  flextable() %>%
  set_caption("ANCOVA for crop biomass response. Crop biomass was analyzed on the original scale.")
```

```{r anova, include=FALSE}
#Make a side by side table 
crops.anova <- joint_tests(crops.lm2) %>% print(export = TRUE)
weeds.anova <- joint_tests(weeds.lm2) %>% print(export = TRUE)
```

```{r, eval=FALSE, include=FALSE}
cbind( weeds.anova$summary, crops.anova$summary) %>%
  kable(caption = "ANOVA tables of crop and weed responses") %>%
  add_header_above(c(" " = 1,  "Weed" = 5, "Crop" = 5))
```

```{r anova-weeds, echo=FALSE}
weeds.anova.df <- as.data.frame(weeds.anova$summary)

weeds.anova.df %>%
  flextable() %>%
  set_caption("ANOVA for weed biomass response. Weed biomass was transformed with ln(x + 1) to maintain data normality.")

plot(emmeans(weeds.lm2, "species.y"), comparisons = TRUE) + 
  xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment") #+ scale_y_discrete(labels = crops_labels)
```

```{r anova-crops, echo=FALSE}
crops.anova.df <- as.data.frame(crops.anova$summary)

crops.anova.df %>%
  flextable() %>%
  set_caption("ANOVA for crop biomass response. Crop biomass was analyzed on the original scale.")
```


```{r, echo=FALSE}
#weeds.emm <- emmeans(weeds.lm1, "treatment", type = "response")

weeds.emm <- emmeans(weeds.lm1, "species.y", type = "response")


#weeds.emm 

# emmip(weeds.lm, treatment ~ crop.biomass.g.per.sq.m, cov.reduce = range)

##levels from PlotMap sheet in Info File_FrosSeededBrassicas_Musgrave 2022
weeds_labels <- c("Radish",
"Turnip",
"Rapeseed",
"Collard", 
"Broadleaf mustard",
"Mustard",
"Brown mustard", 
"Oriental mustard",
"Arugula",
"Winter camelina",
"Kale",
"Red clover",
"Control")



crops_labels <- c("Radish",
"Turnip",
"Rapeseed",
"Collard", 
"Broadleaf mustard",
"Mustard",
"Brown mustard", 
"Oriental mustard",
"Arugula",
"Winter camelina",
"Kale",
"Red clover")
```

Estimated marginal means of weed and crop biomass in each treatment are shown in Figures \@ref(fig:weed-contrast) and \@ref(fig:crop-contrast).    


```{r weed-contrast, echo=FALSE, fig.cap= "Estimated marginal means of weed biomass (back transformed from ln(x +1)). The error bars represent 1 sd on each side."}

weeds.emmip <- emmip(weeds.lm1, ~ species.y, type = "response", plotit = FALSE)


weeds.emmip %>% 
  mutate(sd = 2*SE) %>%
  ggplot(aes(x = species.y, y = yvar)) +
  geom_bar(stat="identity") + 
  geom_errorbar( aes(x = species.y, ymin=yvar-sd, ymax=yvar+sd), width=0.4, colour="orange", alpha=0.9, size=1.3) + 
  ylab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  xlab("Treatment") + scale_x_discrete(guide = guide_axis(angle = 40)) #, labels = weeds_labels)
  
```




```{r crop-contrast, echo=FALSE, fig.cap= "Estimated marginal means of crop biomass. The error bars represent 1 sd on each side."}
crops.emmip <- emmip(crops.lm1, ~ species.y , type = "response", plotit = FALSE)
crops.emmip %>% 
  mutate(sd = 2*SE) %>%
  ggplot(aes(x = species.y, y = yvar)) +
  geom_bar(stat="identity", fill = "#222222") + 
  geom_errorbar( aes(x = species.y, ymin = yvar-sd, ymax = yvar+sd), width=0.4, colour="#B31B1B", alpha=0.9, size=1.3) + 
  ylab(expression(paste("Crop biomass (",g~m^{"-2"},")"))) +
  xlab("Treatment")  + scale_x_discrete(guide = guide_axis(angle = 40)) #, labels = crops_labels)
```

The arrow plots below (Figures \@ref(fig:weed-emmip) and \@ref(fig:crop-emmip)) convey the same information with the bar charts, but are quicker to make. 

```{r weed-emmip, echo = FALSE, fig.cap= "Estimated marginal means of weed biomass (back transformed from ln(x +1)). The black dots are the estimated marginal means. The blue bars indicate the estimated 95% confidence intervals. The arrows indicate whether two estimated means were significantly different. Overlapping arrows means non-significant difference."}
## emmip
# plot(emmeans(weeds.lm, "treatment", type = "response"), comparisons = TRUE) + 
#   xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
#   ylab("Treatment")


plot(emmeans(weeds.lm1, "species.y", type = "response"), comparisons = TRUE) + 
  xlab(expression(paste("Weed biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment") #+ scale_y_discrete(labels = weeds_labels)
```

```{r crop-emmip, echo = FALSE, fig.cap= "Estimated marginal means of crop biomass. The blue bars indicate the estimated 95% confidence intervals. The black dots are the estimated marginal means. The arrows indicate whether two estimated means were significantly different. Overlapping arrows means non-significant difference."}
plot(emmeans(crops.lm1, "species.y"), comparisons = TRUE) + 
  xlab(expression(paste("Crop biomass (",g~m^{"-2"},")"))) +
  ylab("Treatment") #+ scale_y_discrete(labels = crops_labels)
```